Predicting information integration in pragmatic word learning across development

### 2020-11-18 papers/full_paper/models.Rmd
save AIS samples to run on cluster

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll

@@

```{r}
# child_ex3_pragm_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_pragm_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

var steps = 5000
var samples = 100
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

```{r model loglike ex3 children}
# calculating model log-likelihoods

# child_ex3_model_comparison <- bind_rows(
#   child_ex3_pragm_model_likelihood,
#   child_ex3_pragm_model_noise_likelihood,
#   child_ex3_pragm_model_developmental_noise_likelihood,
#   child_ex3_flat_prior_model_noise_likelihood,
#   child_ex3_flat_prior_model_likelihood,
#   child_ex3_flat_prior_model_developmental_noise_likelihood,
#   child_ex3_prior_only_model_noise_likelihood,
#   child_ex3_prior_only_model_likelihood,
#   child_ex3_prior_only_model_developmental_noise_likelihood
# )%>%
#   ungroup()%>%
#   mutate(model = reorder(model,logP))%>%
#   saveRDS("../../stats/saves/child_ex3_model_comparison.rds")

@@

```{r plot model loglikes ex3 children, include = T}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  facet_grid(~parameter)+
  ylim(-475,-400)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))

>>>>

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prag_param_free.csv"
var modelVariant = "integration parameter free"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
#   packages ="webppl-csv",
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
#   mutate(model = "pragmatic",
#          parameter = "parameter free")%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")

child_ex3_pragm_model_likelihood_marginal <- child_ex3_pragm_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prag_noise.csv"
var modelVariant = "integration noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

// var mll = AIS(model, {steps:steps, samples: samples})
// mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
  mutate(model = "pragmatic",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

child_ex3_pragm_model_noise_likelihood_marginal <- child_ex3_pragm_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prag_dev_noise.csv"
var modelVariant = "integration dev noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
  mutate(model = "pragmatic",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood_marginal <- child_ex3_pragm_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_flat_prior_param_free.csv"
var modelVariant = "flat prior parameter free"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
  mutate(model = "flat_prior",
         parameter = "parameter free")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

child_ex3_flat_prior_model_likelihood_marginal <- child_ex3_flat_prior_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_flat_prior_noise.csv"
var modelVariant = "flat prior noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
  mutate(model = "flat_prior",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

child_ex3_flat_prior_model_noise_likelihood_marginal <- child_ex3_flat_prior_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_flat_prior_dev_noise.csv"
var modelVariant = "flat prior dev noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
  mutate(model = "flat_prior",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

child_ex3_flat_prior_model_developmental_noise_likelihood_marginal <- child_ex3_flat_prior_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prior_only_param_free.csv"
var modelVariant = "prior only parameter free"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
  mutate(model = "prior_only",
         parameter = "parameter free")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

child_ex3_prior_only_model_likelihood_marginal <- child_ex3_prior_only_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prior_only_noise.csv"
var modelVariant = "prior only noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
  mutate(model = "prior_only",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood_marginal <- child_ex3_prior_only_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

var steps = 10
var samples = 10

var resultsOutFile = "../../stats/data/llh_child_prior_only_dev_noise.csv"
var modelVariant = "prior only developmental noise"
 var fileHandle = webpplCsv.openFile(resultsOutFile)
 var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
 webpplCsv.writeLine(header_to_write,fileHandle)
 var weights = map(function(i) {
	 var weight = AIS(model, {samples: 1, steps: steps})
	 var line_to_write = [modelVariant, steps, i, weight].join(",")
 	 webpplCsv.writeLine(line_to_write,fileHandle)
 }, _.range(samples))

//var mll = AIS(model, {steps:steps, samples: samples})
//mll
'
```

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
  mutate(model = "prior_only",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

child_ex3_prior_only_model_developmental_noise_likelihood_marginal <- child_ex3_prior_only_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

```{r model loglike ex3 children}
# combining model log-likelihoods

child_ex3_model_comparison <- bind_rows(
  child_ex3_pragm_model_likelihood_marginal,
  child_ex3_pragm_model_noise_likelihood_marginal,
  child_ex3_pragm_model_developmental_noise_likelihood_marginal,
  child_ex3_flat_prior_model_noise_likelihood_marginal,
  child_ex3_flat_prior_model_likelihood_marginal,
  child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
  child_ex3_prior_only_model_noise_likelihood_marginal,
  child_ex3_prior_only_model_likelihood_marginal,
  child_ex3_prior_only_model_developmental_noise_likelihood_marginal
)%>%
  ungroup()%>%
  mutate(model = reorder(model,logP))%>%
  saveRDS("../../stats/saves/child_ex3_model_comparison.rds")

@@

#### Means
```{r plot model loglikes ex3 children, include = T}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  facet_grid(~parameter)+
  ylim(-550,-400)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))

```
#### Likelihood distributions (noise models only)

```{r}
child_ex3_model_ll_dist <- bind_rows(
  child_ex3_pragm_model_likelihood,
  child_ex3_pragm_model_noise_likelihood,
  child_ex3_pragm_model_developmental_noise_likelihood,
  child_ex3_flat_prior_model_noise_likelihood,
  child_ex3_flat_prior_model_likelihood,
  child_ex3_flat_prior_model_developmental_noise_likelihood,
  child_ex3_prior_only_model_noise_likelihood,
  child_ex3_prior_only_model_likelihood,
  child_ex3_prior_only_model_developmental_noise_likelihood
)%>%
  ungroup()%>%
  mutate(model = reorder(model,weight))

ggplot(child_ex3_model_ll_dist, aes(x = weight, col = model, fill = model))+
  geom_histogram(alpha = .5)+
  facet_wrap(~parameter)+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))
